A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-12 sanity/paper1.tex
smaller things
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1073 43ef1190-90fd-4dd7-a769-d0121f02b80e

The companion technical report \cite{kjernsmo_add_survey_2015}, lists other caching
headers than those mentioned in the introduction. We found
\httph{Pragma} (archaic HTTP 1.0 header) in 287 responses, but except
for two hosts, where they were superfluous, they were only used to
prohibit caching. \httph{Surrogate-Capability} were not observed.

@@

In Figure~\ref{fig:hardtable}, we have broken this
up by the type of resource that was accessed, i.e. SPARQL endpoints,
vocabularies, dataset descriptions or unclassified information
resources. First, we note that it seems like the distribution of
freshness lifetime is quite different for the different types, an
observation that is also supported by a similar hypothesis test as
above, with a \pvalue = 0.00001. We also note that it is often
prohibited to cache dataset descriptions. This is odd, since
statistics about datasets is usually costly to compute and should be
cached. The VoID specification \cite{voidnote} also notes that the
statistics are considered estimates.

>>>>

The companion technical report \cite{kjernsmo_add_survey_2015} lists other caching
headers than those mentioned in the introduction. We found
\httph{Pragma} (archaic HTTP 1.0 header) in 287 responses, but except
for two hosts, where they were superfluous, they were only used to
prohibit caching. \httph{Surrogate-Capability} were not observed.

@@

In Figure~\ref{fig:hardtable}, we have broken this
up by the type of resource that was accessed, i.e. SPARQL endpoints,
vocabularies, dataset descriptions or unclassified information
resources. First, we note that it seems like the distribution of
freshness lifetime is quite different for the different types, an
observation that is also supported by a similar hypothesis test as
above, with a \pvalue = 0.00001 (note, however, it is more contrived
than above, since the bins are like in Figure~\ref{fig:hardtable},
which is chosen for intuitive interpretation rather than statistical
rigor). Second, we note that it is often prohibited to cache dataset
descriptions. This is odd, since statistics about datasets is usually
costly to compute and should be cached. The VoID specification
\cite{voidnote} also notes that the statistics are considered
estimates.
